{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-09 thesis/education.tex
spell numbers

\begin{itemize}
	\item A lecture, polished over seven semesters,
		for introducing stateless model checking as a concurrency testing approach
		in high-level undergraduate classes
		(with many slides admittedly specific to Landslide as they may be)
		(\cref{sec:education-pebbles-recruiting}).
	\item A system for automatically instrumenting student thread library (CMU, PSU) and kernel (U. Chicago)
		project implementations to be compatible with stateless model checking
		(\cref{sec:education-pebbles-instrumentation},
		\cref{sec:education-pintos-instrumentation}).
	\item An experimental procedure for evaluating debugging and verification tools
		as student-accessible teaching aids,
		including a survey for measuring the more intangible human experience
		(\cref{sec:education-survey-pebbles},
		\cref{sec:education-survey-pintos}).
	\item A large evaluation spanning 9 semesters of operating systems classes
		(\cref{sec:education-eval-bugfinding}),
		2 of which were held at other universities besides CMU,
		in which 145 students used Landslide,
		a majority of which found bugs (\cref{sec:education-eval-bugfinding}),
		and a vast majority of which expressed via the survey that they had a good experience
		(\cref{sec:education-eval-survey}).
	\item A thorough statistical analysis of Landslide's effect on student submission quality
		(\cref{sec:education-eval-grades}),
		evaluating both impact on ultimate project grades
		and student tendency to submit any of four well-known case study bugs.
		Ultimately, while positive trends were observed,
		this study concluded that a statistically-significant conclusion could not be drawn
		while simultaneously compensating for several obvious sources of possible bias.
		Nevertheless, this level of statistical rigor is not yet widespread in computer science research,
		so I would hope this study may set a precedent that help mature the field.
	\item Concrete action taken to establish Landslide
		as a permanent fixture of 15-410's grading process at CMU,
		student-oriented user guides should the course staff wish it to remain available as a debugging tool,
		as well as general recommendations for any Pintos-based OS class
		at other universities to use it for grading as well
		(\cref{sec:education-future-use}).
\end{itemize}
}

>>>>

\begin{itemize}
	\item A lecture, polished over seven semesters,
		for introducing stateless model checking as a concurrency testing approach
		in high-level undergraduate classes
		(with many slides admittedly specific to Landslide as they may be)
		(\cref{sec:education-pebbles-recruiting}).
	\item A system for automatically instrumenting student thread library (CMU, PSU) and kernel (U. Chicago)
		project implementations to be compatible with stateless model checking
		(\cref{sec:education-pebbles-instrumentation},
		\cref{sec:education-pintos-instrumentation}).
	\item An experimental procedure for evaluating debugging and verification tools
		as student-accessible teaching aids,
		including a survey for measuring the more intangible human experience
		(\cref{sec:education-survey-pebbles},
		\cref{sec:education-survey-pintos}).
	\item A large evaluation spanning nine semesters of operating systems classes
		(\cref{sec:education-eval-bugfinding}),
		two of which were held at other universities besides CMU,
		in which 145 students used Landslide,
		a majority of which found bugs (\cref{sec:education-eval-bugfinding}),
		and a vast majority of which expressed via the survey that they had a good experience
		(\cref{sec:education-eval-survey}).
	\item A thorough statistical analysis of Landslide's effect on student submission quality
		(\cref{sec:education-eval-grades}),
		evaluating both impact on ultimate project grades
		and student tendency to submit any of four well-known case study bugs.
		Ultimately, while positive trends were observed,
		this study concluded that a statistically-significant conclusion could not be drawn
		while simultaneously compensating for several obvious sources of possible bias.
		Nevertheless, this level of statistical rigor is not yet widespread in computer science research,
		so I would hope this study may set a precedent that help mature the field.
	\item Concrete action taken to establish Landslide
		as a permanent fixture of 15-410's grading process at CMU,
		student-oriented user guides should the course staff wish it to remain available as a debugging tool,
		as well as general recommendations for any Pintos-based OS class
		at other universities to use it for grading as well
		(\cref{sec:education-future-use}).
\end{itemize}
}
